Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-22 MS_revised.tex
table 3

% Table 3
\begin{table}[!h]
    \caption{\bf{Likelihood ratio test between the model of increased
diversification of nymphalids feeding on Solanaceae against a model
forcing equal speciation rates (no effect on diversification).}}
\begin{tabular}{lcrrlr}
Df           & lnLik & AIC     & ChiSq  & \multicolumn{1}{r}{p} &         \\
full         & 6     & -1613.3 & 3238.5 &                       &         \\
equal.lambda & 5     & -1619.4 & 3248.9 & 12.3                  & 0.00045
\end{tabular}
\end{table}

>>>>

% Table 3
\begin{table}[!ht]
% \begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
    \caption{{\bf Likelihood ratio test between the model of increased
diversification of nymphalids feeding on Solanaceae against a model
forcing equal speciation rates (no effect on diversification).}}
\begin{tabular}{|l|c|r|r|l|r|}
    \hline
Df           & lnLik & AIC     & ChiSq  & \multicolumn{1}{r}{p} &         \\ \hline
full         & 6     & -1613.3 & 3238.5 &                       &         \\ \hline
equal.lambda & 5     & -1619.4 & 3248.9 & 12.3                  & 0.00045 \\ \hline
\end{tabular}
\begin{flushleft}
\end{flushleft}
\label{table3}
% \end{adjustwidth}
\end{table}
